---
title: "Politics"
date: "2022-10-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages and data to load
```{r packages, message=FALSE}
library(rtweet)
library(dplyr)
library(lubridate)
library(stringr)
library(readr)
library(tidytext)
library(rvest)
library(httr)
data("stop_words")
```

## Twitter

Accessing tweets from all the political parties holding seats in the UK House of Commons.

These are:

* Conservative Party
* Labour Party
* Scottish National Party (Scotland)
* Liberal Democrats
* Democratic Union Party (Northern Ireland)
* Plaid Cymru (Wales)
* Social Democratic Party (Northern Ireland)
* Alba Party (Scotland)
* Alliance Party (Northern Ireland)
* Green Party
* Sinn Féin (Northern Ireland, non-sitting, Twitter profile includes Republic of Ireland too)

Some tweets from Plaid Cymru will be in Welsh. Also a possibility of Scots or Irish.

First, accessing the data from the API. This will not be run whilst knitting the document as the data has now been saved in a CSV file.

```{r download data, eval=FALSE}
# Read in tweets once, and then save as a file for speed

con_tweets <- get_timeline("Conservatives", n = 3200)
lab_tweets <- get_timeline("UKLabour", n = 3200)
snp_tweets <- get_timeline("theSNP", n = 3200)
libdem_tweets <- get_timeline("LibDems", n = 3200)
dup_tweets <- get_timeline("duponline", n = 3200)
plaid_tweets <- get_timeline("Plaid_Cymru", n = 3200)
sdp_tweets <- get_timeline("SDPhq", n = 3200)
alba_tweets <- get_timeline("AlbaParty", n = 3200)
alliance_tweets <- get_timeline("allianceparty", n = 3200)
green_tweets <- get_timeline("TheGreenParty", n = 3200)
sf_tweets <- get_timeline("sinnfeinireland", n = 3200)

# Creating a single data frame for storage
data_list <- list('con_tweets', 'lab_tweets', 'snp_tweets', 'libdem_tweets', 'dup_tweets', 'plaid_tweets', 'sdp_tweets', 'alba_tweets', 'alliance_tweets', 'green_tweets', 'sf_tweets')

hoc_working <- tibble(created_at = POSIXct(),
                      party = character(),
                      text = character(),
                      favorite_count = integer(),
                      retweet_count = integer())

for (x in data_list) {
  add_tweets <- get(x) %>%
    filter(retweeted == "FALSE") %>%
    mutate(party = str_remove(x, '_tweets')) %>% 
    select(created_at, party, text, favorite_count, retweet_count)
  
  hoc_working <-
    hoc_working %>%
    bind_rows(add_tweets)
}

hoc_tweets <-
  hoc_working %>%
  filter(str_starts(text, 'RT', negate = T)) %>% # Not sure why retweet flag didn't work
  # Handling tweets in Welsh or Gaelic
  mutate(lang = cld2::detect_language(text)) %>%
  filter(lang == 'en') %>%
  select(-lang) %>%
  mutate(party = case_when(party=='con' ~ 'Conservatives',
                           party=='lab' ~ 'Labour',
                           party=='libdem' ~ 'Liberal Democrats',
                           party=='snp' ~ 'Scottish National Party',
                           party=='dup' ~ 'Democratic Unionist Party',
                           party=='plaid' ~ 'Plaid Cymru',
                           party=='sdp' ~ 'Social Democratic Party',
                           party=='alba' ~ 'Alba',
                           party=='alliance' ~ 'Alliance',
                           party=='green' ~ 'Green',
                           party=='sf' ~ 'Sinn Féin'))
  
# Save data to a CSV
readr::write_csv(hoc_tweets, 'hoc_tweets_221003.csv')
```

The main parties all returned 3200 tweets from the request. Some of the smaller parties had fewer tweets in the initial sample eg. Alba Party as was only founded in 2021. All retweets have then been removed.

Then processing the data to look at the most frequent words by party. This uses the data that has already been saved in a CSV.

```{r process data, message=FALSE}
hoc_tweets <- readr::read_csv('hoc_tweets_221003.csv')

clean_hoc_tweets <-
  hoc_tweets %>%
  mutate(
    # identify tweets with hashtags
    has_tag = str_detect(text, "#\\w+"),
    # how many at-mentions are there?
    n_at = str_count(text, "(^|\\s)@\\w+"),
    # extract first url
    url = str_extract(text, "(https?://\\S+)"),
    # remove at-mentions, tags, and urls
    clean_text = 
      str_replace_all(text, "(^|\\s)(@|#|https?://)\\S+", " ") %>% 
      str_replace_all("\\W+", " "))

tokens <-
  clean_hoc_tweets %>%
  unnest_tokens(word, clean_text) %>%
  select(party, word) %>%
  anti_join(stop_words) %>%
  count(word, party, sort = TRUE)

top_tokens <-
  tokens %>%
  group_by(party) %>%
  slice_max(order_by=n, n=10) %>% # Keep top 10 tokens by party
  ungroup()

tweets_by_party <-
  clean_hoc_tweets %>%
  count(party)

tweets_by_party
top_tokens %>% filter(party=='Conservatives') # Most common tokens used by the Conservatives
top_tokens %>% filter(party=='Labour')        # Most common tokens used by Labour
top_tokens %>% count(word) %>% filter(n>2)
```

The Conservatives twitter account produces far fewer original tweets than any other party. Of the 3200 tweets downloaded, only 420 were not retweets. Sinn Féin produce significantly more original tweets than any other party. This could potentially be related to the frequency with which their individual politicians use Twitter. For the Conservatives, some of their original Tweets may be published using official Government Twitter accounts and they then retweet those tweets.

The appearence of '000' in the most popular words for the Conservatives is due to their use of large numbers written in full eg. 100,000.

Many of the parties have the Conservatives ('conservatives', 'tories', 'tory', and sometimes 'government') referenced in their 10 most frequent words. The Conservatives are an exception to this, but do include mention of Labour ('labour'). 'people' was in the most popular words for 10 of the 11 parties (only not appearing for the DUP).
