---
title: "Using STED"
date: "2022-10-22"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(purrr)
library(readr)
library(stringr)
library(quanteda)
library(jsonlite)
library(tibble)
library(tidyr)
library(ggplot2)
library(scales)
```

## Loading data

Data sources have been chosen such that they are expected to have low and high potential for meaningful entertainment experiences respectively. The first is Hansard (record of UK Parliament) and the second is Eurovision Song Contest lyrics.

[https://hansard.parliament.uk/commons/2022-10-20](https://hansard.parliament.uk/commons/2022-10-20)
[https://www.kaggle.com/datasets/minitree/eurovision-song-lyrics?resource=download](https://www.kaggle.com/datasets/minitree/eurovision-song-lyrics?resource=download)

### Hansard

Data has been retrieved for the debates in the lower house in October 2022. With more care, the words of each individual could be identified separately. However, here each day is considered separately.

```{r hansard load}
filenames <- tibble('long' = list.files(path = './hansard_data/', pattern="*.txt", full.names = T),
                    'short' = list.files(path = './hansard_data', pattern="*.txt"))

hansard_raw <- tibble(date = as.Date(character()),
                  text = character())

for (i in 1:length(filenames$long)){
  new_text = read_file(filenames$long[i])
  new_row = tibble(
    date = filenames$short[i] %>% str_remove("Commons Chamber ") %>% str_remove(".txt") %>% as.Date(),
    text = new_text)
  hansard_raw <- bind_rows(hansard_raw, new_row)}

hansard <-
  corpus(hansard_raw,
         docid_field = "date",
         text_field = "text") %>%
  quanteda::tokens(remove_punct = TRUE, 
                   remove_numbers = TRUE, 
                   remove_symbols = TRUE,
                   remove_url = TRUE) %>% 
  tokens_tolower() %>%
  tokens_remove(stopwords("english")) %>%
  tokens_wordstem()
```

## Eurovision lyrics

The lyrics are provided in their original language and with a translation too. Here the English translation will be used where the original song was in another language.

```{r eurovision load}
esc_raw <- jsonlite::fromJSON(txt="eurovision-lyrics-2022.json") 

esc_data <- tibble(song_id = character(), 
                   country = character(), 
                   name = character(), 
                   language = character(), 
                   year = character(), 
                   lyrics = character())

for (i in 1:length(esc_raw)){
  new_data = esc_raw[[i]]
  new_row = tibble(song_id = new_data[[1]],
                   country = new_data[[2]],
                   name = new_data[[5]],
                   language = new_data[[6]],
                   year = new_data[[10]],
                   lyrics = if_else(new_data[[14]]=="English", new_data[[13]], new_data[[14]]))
  esc_data <- bind_rows(esc_data, new_row)}

esc <-
  corpus(esc_data,
         docid_field = "song_id",
         text_field = "lyrics") %>%
  quanteda::tokens(remove_punct = TRUE, 
                   remove_numbers = TRUE, 
                   remove_symbols = TRUE,
                   remove_url = TRUE) %>% 
  tokens_tolower() %>%
  tokens_remove(stopwords("english")) %>%
  tokens_wordstem()
```

## STED

### Hansard
```{r hansard sted}
sted_dict <- dictionary(file = "pone.0239050.s003.dic", format = "LIWC")

hansard_sted <- 
  tokens_lookup(hansard, dictionary = sted_dict) %>%
  dfm() %>%
  dfm_group()

hansard_sted_df <- convert(hansard_sted, to = "data.frame")

hansard_all_df <- hansard %>%
  ntoken() %>%
  as.data.frame() %>%
  rownames_to_column(var = "doc_id") %>%
  rename("tokens" = ".")

hansard_final <-
  hansard_sted_df %>%
  left_join(hansard_all_df, by = 'doc_id') %>%
  mutate(general = general/tokens,
         awe = awe/tokens,
         gratitude = gratitude/tokens,
         elevation = elevation/tokens,
         admiration = admiration/tokens,
         hope = hope/tokens,
         doc_id = as.Date(doc_id)) %>%
  select(-tokens) %>%
  pivot_longer(
    cols = !doc_id)

```

### Eurovision STED
```{r eurovision sted}

esc_sted <- 
  tokens_lookup(esc, dictionary = sted_dict) %>%
  dfm() %>%
  dfm_group(group = year)

esc_sted_df <- convert(esc_sted, to = "data.frame")
esc_all_df <-
  esc %>%
  tokens_group(groups = year) %>%
  ntoken() %>%
  as.data.frame() %>%
  rownames_to_column(var = "doc_id") %>%
  rename("tokens" = ".")

esc_final <-
  esc_sted_df %>%
  left_join(esc_all_df, by = 'doc_id') %>%
  mutate(general = general/tokens,
         awe = awe/tokens,
         gratitude = gratitude/tokens,
         elevation = elevation/tokens,
         admiration = admiration/tokens,
         hope = hope/tokens,
         doc_id = as.numeric(doc_id)) %>%
  select(-tokens) %>%
  pivot_longer(
    cols = !doc_id)

```

## Plots

### Hansard

```{r hansard plot}
ggplot(hansard_final, aes(x = doc_id, y = value, group = name, colour = name)) +
  geom_line(size=1, lineend="round") +
  scale_y_continuous(
    limits = c(0,0.02),
    labels = label_percent(),
    expand = c(0,0)) +
  scale_x_date(
    date_labels = "%d %b",
    expand = c(0,0)) +
  theme_minimal() +
  theme(legend.title=element_blank(),
        axis.title = element_blank(),
        axis.line = element_line(size = 0.5, colour = "grey60"),
        panel.grid.minor = element_blank()) +
  labs(
    title = "Percentage of self-transcendent emotion words in Hansard",
    subtitle = "In October 2022")


```

### Eurovision

```{r eurovision plot}
ggplot(esc_final, aes(x = doc_id, y = value, group = name, colour = name)) +
  geom_line(size=1, lineend="round") +
  scale_y_continuous(
    limits = c(0,0.08),
    labels = label_percent(),
    expand = c(0,0)) +
  theme_minimal() +
  theme(legend.title=element_blank(),
        axis.title = element_blank(),
        axis.line = element_line(size = 0.5, colour = "grey60"),
        panel.grid.minor = element_blank()) +
  labs(
    title = "Percentage of self-transcendent emotion words in Eurovision Song Contest lyrics",
    subtitle = "By year")


```

## Examples

### Individual countries' Eurovision songs

```{r eurovision sted2}
esc$year_country <- paste0(esc$year, " ", esc$country)

esc_sted2 <- 
  tokens_lookup(esc, dictionary = sted_dict) %>%
  dfm() %>%
  dfm_group(group = year_country)

esc_sted_df2 <- 
  convert(esc_sted2, to = "data.frame") %>%
  mutate(year = as.numeric(str_extract(doc_id, "[0-9]{4}")),
         country = str_remove(doc_id, "[0-9]{4} ")) %>%
  select(-doc_id)
esc_all_df2 <-
  esc %>%
  tokens_group(groups = year_country) %>%
  ntoken() %>%
  as.data.frame() %>%
  rownames_to_column(var = "doc_id") %>%
  rename("tokens" = ".") %>%
  mutate(year = as.numeric(str_extract(doc_id, "[0-9]{4}")),
         country = str_remove(doc_id, "[0-9]{4} ")) %>%
  select(-doc_id)

esc_final2 <-
  esc_sted_df2 %>%
  left_join(esc_all_df2, by = c('year', 'country')) %>%
  mutate(general = general/tokens,
         awe = awe/tokens,
         gratitude = gratitude/tokens,
         elevation = elevation/tokens,
         admiration = admiration/tokens,
         hope = hope/tokens) %>%
  select(-tokens) %>%
  pivot_longer(
    cols = !c(year, country)) %>%
  mutate(country = case_when(country=="The Netherlands" ~ "Netherlands",
                             str_detect(country, "Germany") ~ "Germany",
                             T ~ country))

```

#### Germany vs UK

```{r germany uk}
esc_final2 %>%
  filter(country %in% c("Germany", "United Kingdom")) %>%
ggplot(aes(x = year, y = value, group = country, colour = country)) +
  geom_line() +
  scale_y_continuous(
    limits = c(0,0.2),
    labels = label_percent(),
    expand = c(0,0)) +
  theme_minimal() +
  theme(legend.title=element_blank(),
        axis.title = element_blank(),
        axis.line = element_line(size = 0.5, colour = "grey60"),
        panel.grid.minor = element_blank()) +
  labs(title = "Percentage of self-transcendent emotion words in Eurovision Song Contest lyrics",) +
  facet_wrap(~ name, nrow = 3)


```
### Songs with no STED identified
```{r }
esc_no_sted <- 
  esc_final2 %>% 
  group_by(year, country) %>% 
  summarise(sum = sum(value)) %>% 
  filter(sum==0)

ggplot(esc_no_sted, aes(x = year)) +
  geom_bar() +
  theme_minimal() +
  scale_y_continuous(
    expand = c(0,0),
    limits = c(0,5)) +
  theme(legend.title=element_blank(),
        axis.title = element_blank(),
        axis.line = element_line(size = 0.5, colour = "grey60"),
        panel.grid.minor = element_blank()) +
  labs(
    title = "Number of Eurovision Song Contest songs with no STED identified in the lyrics",
    subtitle = "(English translation of lyrics)")

```

## Summary

As expected, the rate of self-transcendent emotion words was much lower in the Hansard records of the UK Parliament than in Eurovision song lyrics. In parliament, hope was generally the most identified self-transcendent emotion, but all of the emotion types remained at below 2% of all words (after stop word removal). In contrast, many Eurovision songs had values above 15%. There is significant variation across songs but most have more awe, admiration and hope than elevation, general or gratitude.

72 of the songs have not been labelled with any self-transcendent emotions. These include "Der K und K Kalypso aus Wien" for Austria in 1959 with lyrics including "The Calypso from Vienna. It's not from Ecuador. It's not from Spain." and "Higher Ground" for Denmark in 2018 with lyrics including "Freeze the arrow in the air. Make your mark and leave it hanging there."








